Estimation of Stochastic Wilson and Cowan Neural Field Model using Expectation Maximisation Algorithm

### 2011-08-04 ltx/data_paper/DataPaper.tex
minor edit

Complex conjugate operator essentially reflects the connectivity kernel through the origin in the spatial domain, therefore, if the connectivity kernel is isotropic, the complex conjugate operator can be dropped. 

>>>>

The complex conjugate operator essentially reflects the connectivity kernel through the origin in the spatial domain, therefore, if the connectivity kernel is isotropic, the complex conjugate operator can be dropped. 
